---
title: "Project Report"
author: "Will Ju"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# BRFSS Data Science Project Report

## Introduction

This is a toy project report for the BRFSS data <https://ds202-at-isu.github.io/materials/01_collaborative-environment/data/brfss_iowa.csv>

Our goal is to investigate the relationship between **height** and **weight**

## Data

Here we import the data from a csv file

```{r}
data <- read.csv("data/brfss_iowa.csv")
```

Then we check the number of variables and observations

```{r}
dim(data)

head(data)
```

Then we check the variable `HEIGHT3` and `WEIGHT2`

```{r}

```

## Correlation

We want to investigate the xxx by gender

```{r}
male_data <- data
female_data <- data
```

Then we found that the

## Conclusion

For this project, we ...

-   point 1

-   point 2

-   **bold font**

-   *italic*

1.  list item 1
2.  list item 2














